Lens Modeling in \sw

### 2013-09-09 text/tex/results.tex

>>>>

In \figref{eR_all} can be seen, that the calculated einstein radius $\Theta_E$ of the models tend to be too high.
The overshoot varies from around 0.2 to 0.4 for for good models.
One of the reasons for this is, that it's hard to get the center of the lens on spot.
An offset leads to a a flatter mass profile for the model compared to the simulation.
